\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 appendix.tex
Mark main screen graphic for referencing the UI components

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.9\linewidth]{screenshots/main_screen}
% \vspace{-5pt}
\caption{Main Screen of J-ReCoVer}
\label{fig:main_screen}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{itemize}
\item
Top Menu:
\begin{itemize}
\item
\emph{``GitHub''} opens a new tab of the repository of J-ReCoVer. The repository also has source code of benchmarks.
\item
\emph{``Benchmark''} leads to the list of benchmarks we collected with their results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows. Select the filename or "try it" button will select the example and go back to the main screen.
\end{itemize}
\item
Right Menu:
\begin{itemize}
\item
\emph{``Benchmark List''} provides a quick selection to examples in the benchmark (Fig.~\ref{fig:benchmark_list_right})
\item
\emph{``Results''} shows the last analysis result.
\end{itemize}
\item
Upper-Right Menu:
\begin{itemize}
\item
\emph{``Type''} provides types that J-ReCoVer supports. Details are explained in~\ref{appendix:3}.
\item
\emph{``Run''} starts the analysis of the selected example.
\end{itemize}
\item
Upper-Left Menu: See~\ref{appendix:3}.
\end{itemize}

@@

\subsection{Run analysis of an example from sketch}
\label{appendix:3}

Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyse a user defined reducer function.
The upper-left menu (below the top menu) provides blank templates for two versions of Hadoop. The templates are

>>>>

\begin{figure}
\begin{center}
% \vspace{-10pt}
\includegraphics[width=.9\linewidth]{screenshots/main_screen_marked}
% \vspace{-5pt}
\caption{Main Screen of J-ReCoVer}
\label{fig:main_screen}
% \vspace{-15pt}
\end{center}
\end{figure}

\begin{itemize}
\item
Top Menu:
\begin{itemize}
\item
\emph{``GitHub''} opens a new tab of the repository of J-ReCoVer. The repository also has source code of benchmarks.
\item
\emph{``Benchmark''} leads to the list of benchmarks we collected with their results of commutativity analysis as Fig.~\ref{fig:benchmark_list} shows. Select the filename or "try it" button will select the example and go back to the main screen.
\end{itemize}
\item
Right Menu:
\begin{itemize}
\item
\emph{``Benchmark List''} provides a quick selection to examples in the benchmark (Fig.~\ref{fig:benchmark_list_right})
\item
\emph{``Results''} shows the last analysis result.
\end{itemize}
\item
Upper-Right Menu:
\begin{itemize}
\item
\emph{``Type''} provides types that J-ReCoVer supports. Details are explained in~\ref{appendix:3}.
\item
\emph{``Run''} starts the analysis of the selected example.
\end{itemize}
\item
Upper-Left Menu: See~\ref{appendix:3}.
\item
Coding Space
\end{itemize}

@@

\clearpage
\subsection{Run analysis of a user-defined reducer function}
\label{appendix:3}

Besides examples from the benchmark, J-ReCoVer also provides an interactive way to analyse a user-defined reducer function. 
One can directly edit the code of a selected example in the coding space for further analysis, or write a reducer function from a sketch. 
The upper-left menu (below the top menu) provides blank templates for two versions of Hadoop. The templates are
